\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage [a4paper, left=2.5cm, right=2.5cm] {geometry}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{longtable}
\usepackage{verbatim}

\geometry{a4paper}

\numberwithin{figure}{section}
\numberwithin{table}{section}

\begin{titlepage}

\title{Design Document (DD)}
\author{Group Name: Davide Rodler, Stefano Riva \\ Version: 1.0 \\ Date: [Submission Date]}
\date{}

\end{titlepage}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Introduction}

\subsection{Purpose}
The \textbf{Students\&Companies (S\&C)} platform aims to simplify the process of connecting university students with companies offering internships. For students, finding internships that match their skills and career goals can often be challenging, while companies may struggle to identify candidates with the right qualifications.

This platform provides students with tools to search for internships, receive personalized recommendations, and manage their applications. At the same time, companies can use it to advertise internships, review student CVs, and organize interviews efficiently. By incorporating advanced recommendation mechanisms, the platform creates a streamlined and mutually beneficial experience for both parties.

\subsection{Scope}
The S\&C platform is designed for two main types of users: students and companies. 

\begin{itemize}
    \item \textbf{Students}: Students can create and upload their CVs, search for internships, receive personalized recommendations, and track their application progress.
    \item \textbf{Companies}: Companies can advertise internships, search for and evaluate student profiles, schedule interviews, and manage the selection process.
\end{itemize}

Additionally, the platform gathers feedback from both students and companies. This feedback is used to enhance the recommendation system and provide insights into the effectiveness of internships, ensuring continuous improvement of the platform.   

\subsection{Definitions, Acronyms, and Abbreviations}
\subsubsection{Definitions}
\begin{itemize}
    \item \textbf{Curriculum Vitae (CV)}: A document detailing a student's skills, experiences, and educational background.
    \item \textbf{Internship}: A temporary professional opportunity provided by a company to a student, typically aligned with their academic field.
    \item \textbf{Recommendation System}: A feature of the platform that suggests internships to students and candidates to companies based on advanced matching algorithms.
\end{itemize}

\subsubsection{Acronyms}
\begin{itemize}
    \item \textbf{S\&C}: Students\&Companies platform.
    \item \textbf{CV}: Curriculum Vitae.
\end{itemize}

\subsubsection{Abbreviations}
\begin{itemize}
    \item \textbf{G*}: Goals outlined in the Purpose section.
    \item \textbf{WP*}: World phenomena describing actions by individual stakeholders.
    \item \textbf{SP*}: Shared phenomena describing interactions mediated by the system.
    \item \textbf{R*}: Functional requirements.
    \item \textbf{UC*}: Use cases.
    %INSERIRE GLI ALTRI
\end{itemize}

\subsection{Revision History}
\begin{itemize}
    \item Version 1.0: Initial draft of the document.
\end{itemize}

\subsection{Reference Documents}
\begin{itemize}
    \item Project Specification Document provided by the course instructors.
    \item Course slides available on the university platform.
\end{itemize}

\subsection{Document Structure}
The remainder of this document is organized as follows:
\begin{itemize}
    \item \textbf{Section 1 - Introduction}: Covers the purpose, scope, and definitions of the project.
    \item \textbf{Section 2 - Architectural Design}: %INSERIRE DESCRIZIONE
    \item \textbf{Section 3 - User Interface Design}: %INSERIRE DESCRIZIONE
    \item \textbf{Section 4 - Requirements Traceability}: %INSERIRE DESCRIZIONE
    \item \textbf{Section 5 - Implementation, Integration and Test Plan }: %INSERIRE DESCRIZIONE
    \item \textbf{Section 6 - Effort Spent}: Shows the time spent by each group member to realize this document.
    \item \textbf{Section 7 - References}: Contains references to any document or software used during the realization of this document
\end{itemize}

\newpage

\section{Effort Spent}
In this section there's an overview of the time effort spent for each group member to write and revise each chapter of this document.
    \begin{itemize}
        \item \textbf{Davide Rodler}
            \begin{table}[H]
                \centering
                \begin{tabular}{|c|c|}
                    \hline
                    \textbf{Chapter} & \textbf{Effort (in hours)} \\
                    \hline
                    Chapter 1 &  \\
                    \hline
                    Chapter 2 &  \\
                    \hline
                    Chapter 3 &  \\
                    \hline
                    Chapter 4 &  \\
                    \hline
                    Chapter 5 & \\
                \end{tabular}
            \end{table} 
            
        \item \textbf{Stefano Riva}
            \begin{table}[H]
                \centering
                \begin{tabular}{|c|c|}
                    \hline
                    \textbf{Chapter} & \textbf{Effort (in hours)} \\
                    \hline
                    Chapter 1 &  4\\
                    \hline
                    Chapter 2 &  3\\
                    \hline
                    Chapter 3 &  20\\
                    \hline
                    Chapter 4 &  \\
                    \hline
                    Chapter 5 & \\
                \end{tabular}
            \end{table}
    \end{itemize}

\section{Reference \& Used Tools}
\subsection{Paper References}
    \begin{itemize}
        \item Specification document "Assignment RDD AY 2024-2025".
        \item Slides from the Software Engineering 2 course.
    \end{itemize}
\subsection{Used Tools}
    \begin{itemize}
        \item Writing and Drafting the document: Overleaf.
        \item Diagrams drawing: Draw.io.
        \item Mockups mading: %INSERIRE PROGRAMMA.
        \item Versioning: Github.
    \end{itemize}

\listoffigures
\listoftables

\end{document}